---
title: "Capitulo 4"
author: "Pedro Pablo Villegas"
date: "2/10/2019"
output: html_document
---

# GENERACION DE VARIABLES ALEATORIAS DISCRETAS

## Metodo de la transformada inversa

### Variable uniforme discreta

```{r, eval=TRUE, echo=TRUE}

# variable aleatoria discreta -----------

runif.discrete <- function(n, k){ #n simulaciones, k espacios
    u <- runif(n)
    x <- floor(k * u) + 1
    return(x)
}

# permutacion ----------------

permutacion <- function(m) { # m tamaño grupo
    if (m == 1) stop("Error")
        x <- seq(1, m)
        for (i in 2:m) {
            j <- runif.discrete(n = 1, k = i - 1)
            temp <- x[i]
            x[i] <- x[j]
            x[j] <- temp
        }
    x
}
```


# Pagina 50 Simulacion 

Another way to generate a random permutation is to generate n random numbers U1, . . . , Un, order them, and then use the indices of the successive values as the random permutation. For instance, if n = 4, and U1 = 0.4, U2 = 0.1, U3 = 0.8, U4 = 0.7, then, because U2 < U1 < U4 < U3, the random permutation is 2, 1, 4, 3. The difficulty with this approach, however, is that ordering the random numbers typically requires on the order of n log(n) comparisons. 

```{r, eval=TRUE, echo=TRUE}

runif.discrete2 <- function(n){
    res <- matrix(nrow = n, ncol = 2)
    i <- 1
    while (i <= n) {
        res[i, 1] <- i
        res[i, 2] <- runif(1)
        i <- i + 1
    }
    res[order(res[,2])]
}

```

## Geometric distribution

```{r, eval=TRUE, echo=TRUE}

r.geom <- function(n, p) {
    u <- runif(n)
    x <- floor(log(u) / log(1 - p)) + 1
    return(x)
}

```

## Poisson distribution

```{r, eval=TRUE, echo=TRUE}

one.poisson <- function(u, lambda) {
    p <- exp(-lambda)
    F <- p
    i <- 0
    while (u >= F) {
        i <- i + 1
        p <- p * lambda / i
        F <- F + p
        }
    return(i)
}


one.poisson <- Vectorize(one.poisson)

r.pois <- function(n, lambda) {
    one.poisson(runif(n), lambda)
}

```

## Binomial distribution

```{r, eval=TRUE, echo=TRUE}

one.binom <- function(u, p, size) {
    K <- p/(1 - p)
    p <- (1 - p)^size
    Acumul <- p
    i <- 0
    while (u > Acumul) {
        p <- p * K * (size - i)/(i + 1)
        Acumul <- Acumul + p
        i <- i + 1
        }
    return(i)
}

one.binom <- Vectorize(one.binom)

r.binom <- function(n, p, size) {
    one.binom(u = runif(n), p, size)
}

```

# Metodo de aceptacion y rechazo

